\documentclass[11pt]{article}
\usepackage{amsmath, amssymb, amsthm, geometry, bm, booktabs}
\usepackage[hidelinks]{hyperref}
\geometry{margin=1in}

\title{Pair Correlation and Spectral Correspondence in Primorial Lattices:\\
Toward a Geometric Bridge Between Discrete Gap Statistics and the Riemann Zeta Zeros}
\author{Rob Miller}
\date{June 2026}

% RAPF Paper 5 — the spectral bridge paper
% Framework by Rob Miller. Gemini-drafted LaTeX scaffold, patched by Rebecca.

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\begin{document}
\maketitle

\begin{abstract}
Building on the unified structural framework of finite-scale lattice relaxation established in Papers~1--4, this paper initiates the analytical and empirical bridge between the discrete information geometry of primorial lattices and the spectral theory of the Riemann zeta function. We pursue three parallel objectives: (i) the introduction of an $\mathcal{O}(NW)$ windowed streaming histogram operator to extract unfolded pair-correlation statistics from the 128-billion twin prime dataset without memory exhaustion, comparing the results against the Montgomery--Bogomolny--Keating GUE baseline; (ii) the exploration of whether the higher-order Bernoulli-weighted discrete penalties from Paper~4 can constrain the error contributions of non-trivial zeros via the classical explicit formula; and (iii) the derivation of leading-order stability bounds for the $1/\sinh^2$ Fisher metric fixed point under the logarithmic renormalization group flow. Finally, we deploy a Maier-modulated probability mass function to deliver a testable prediction for the coefficient of variation at the uncomputed $n=9$ primorial scale.
\end{abstract}

\noindent \textbf{MSC 2020:} 11N05, 11N36, 62B10, 82B28

\section{Introduction}
The Riemann--von Mangoldt explicit formula provides the foundational nexus connecting prime counting functions directly to the complex zeros $\rho = \frac{1}{2} + i\gamma$ of the Riemann zeta function. Simultaneously, the Hardy--Littlewood $k$-tuples conjecture governs the local density of prime constellations via their singular series baselines. In Papers~1--3 of this program, we established the necessity of discrete lattice geometries over continuous manifold approximations, empirically verifying a universal sub-Poisson variance suppression across twin and triplet admissible residue classes that smoothly relaxes toward Poisson randomness as the primorial moduli scale. Paper~4 unified these case studies into a non-collapsing structural framework parameterized by exact closed-form hyperbolic metrics.

This paper bridges the gap between finite-scale computational phenomenology and spectral analysis. Rather than treating local deviations from continuous heuristics as stochastic noise, we investigate whether these fluctuations carry explicit arithmetic data. We structure this exploration across three main fronts: empirical pair-correlation extraction via windowed streaming operators, investigation of error-term dampening via the Taylor expansion of the discrete Fisher information metric, and localized error trapping along the renormalization group flow.

\noindent\textbf{Remark.} We emphasize that this paper presents spectral investigations and heuristic bridges, not proofs. The connections proposed between the discrete lattice framework and zeta zero distributions are exploratory. Results in Sections~3 and~4 are conjectures supported by structural evidence, not established theorems.

\section{Pair Correlation on Primorial Lattices}

\subsection{Normalization and Unfolding of Gap Data}
To evaluate whether the localized repulsion of prime constellation gaps aligns with the universal Gaussian Unitary Ensemble (GUE) statistical properties governing the non-trivial zeros, raw gap data must undergo a scaling transformation known as unfolding the spectrum.

Let $g_i = q_{i+1} - q_i$ represent the distance between consecutive prime constellations (twins or triplets) restricted to an admissible primorial range $[P_n, P_n^2]$. These gaps are strictly confined to an arithmetic lattice of spacing $d$, where $d=6$ for the modulo-6 twin lattice and $d=30$ for the modulo-30 triplet lattice. Let $\hat{\lambda}_{\mathrm{cum}}(X) = X / (2C_2\,\mathrm{li}_2(X))$ define the cumulative mean gap up to scale $X$. The normalized, dimensionless unfolded gap coordinate $u_i$ is defined by:
\begin{equation}
    u_i = \frac{g_i}{\hat{\lambda}_{\mathrm{cum}}(X)}.
\end{equation}
At finite scales, $u_i$ constitutes a highly discrete rational set. As $X \to \infty$, the normalized step size $\Delta u = d / \hat{\lambda}_{\mathrm{cum}}(X) \to 0$, continuously smoothing the discrete lattice step into the continuous spectral domain.

\subsection{The Empirical Pair-Correlation Streaming Operator}
A standard evaluation of the two-point pair correlation function requires an $\mathcal{O}(N^2)$ cross-distance computation. Given that the Paper~2 census contains $N = 128 \times 10^9$ twin pairs, a naive calculation requires $\sim 1.6 \times 10^{22}$ floating-point operations, causing immediate memory exhaustion.

To bypass this barrier, we introduce a windowed Streaming Histogram Operator $\mathcal{H}_W$. Because lattice-induced correlations drop exponentially over long distances, information-theoretic dependencies are highly localized. We define an active window radius $W \in \mathbb{N}$ (e.g., $W = 1000$). The operator streams raw gaps sequentially through a circular ring buffer, accumulating absolute distances in coordinate space to reconstruct the integrated second-moment density without storing the full cross-distance matrix in system memory.

\subsection{Comparison to Montgomery's GUE Model}
Montgomery's pair-correlation theorem demonstrates that the statistical density of normalized zero spacings approaches the continuous baseline:
\begin{equation}
    R_2(u) = 1 - \left(\frac{\sin(\pi u)}{\pi u}\right)^2.
\end{equation}
When the empirical array processed by $\mathcal{H}_W$ is overlaid against $R_2(u)$, the discrete lattice geometry manifests as peaks at integer multiples of the lattice spacing $d/\hat{\lambda}_{\mathrm{cum}}(X)$. The core structural thesis predicts that as $n \to \infty$, these localized fluctuations decay monotonically, tracking the exact relaxation path of the observed $CV/CV_{\mathrm{Poisson}} \to 1.0$ curve documented in Papers~2 and~3.

\section{Exploring the Explicit Formula Bridge}

\subsection{The Riemann--von Mangoldt Explicit Formula}
The smoothed prime counting function $\psi(X) = \sum_{n \le X} \Lambda(n)$ maps exact arithmetic counts to wave interference patterns generated by the spectrum of non-trivial zeros:
\begin{equation}
    \psi(X) = X - \sum_{\rho} \frac{X^\rho}{\rho} - \ln(2\pi) - \frac{1}{2}\ln(1 - X^{-2}).
\end{equation}
For prime $k$-tuples, no rigorous explicit formula is currently known in the literature. However, the local error term $E(X) = \pi_k(X; \mathcal{H}) - \mathfrak{S}(\mathcal{H})\,\mathrm{li}_k(X)$ for single primes is driven by the spectral wave sum. We ask whether a generalized form might exist for $k$-tuples, potentially modified by the discrete combinatorial topology of the primorial lattice.

\begin{conjecture}[k-Tuple Explicit Formula Structure]
The $k$-tuple error term may admit a decomposition of the form:
\begin{equation}
    E_k(X) \sim \sum_{\gamma} \frac{X^{1/2 + i\gamma}}{\frac{1}{2} + i\gamma} \cdot \Phi_k(\gamma),
\end{equation}
where $\Phi_k(\gamma)$ is a lattice-dependent phase factor encoding the combinatorial filtering structure of $\mathcal{A}_n^{(k)}$. The determination of $\Phi_k$ remains an open problem.
\end{conjecture}

\subsection{Investigating Error Term Bounds via Taylor Penalties}
In Paper~4, we established that the exact closed-form Fisher information metric $I(\lambda)$ expands into a convergent series dominated by alternating discrete penalties:
\begin{equation}
    I(\lambda) = \frac{C}{B^2 \lambda^2} - \frac{C}{3\lambda^4} + \frac{CB^2}{15\lambda^6} - \frac{2CB^4}{189\lambda^8} + \mathcal{O}(\lambda^{-10}).
\end{equation}
The Fisher functional integrates over the second moment of the gap distribution. We conjecture that unbounded growth in a putative $k$-tuple spectral error would distort the variance bounds, potentially violating the metric's closed-form hyperbolic envelope. Under this hypothesis, the first-order discrete penalty $-\frac{C}{3\lambda^4}$ could function as a geometric dampening field, suggesting a bound of the form:
\begin{equation}
    \left| \sum_{|\gamma| \le T} \frac{X^{i\gamma}}{\frac{1}{2} + i\gamma} \right| \; \stackrel{?}{\le}\; \alpha \cdot \sqrt{\frac{3\lambda^4(X)}{C}} + \mathcal{O}\!\left(\frac{1}{T}\right),
\end{equation}
where $\alpha$ is a localized normalization constant. This inequality is conjectural — no rigorous derivation connecting the Fisher metric's Taylor expansion to the explicit formula zero-sum is known at present.

\subsection{Questions Regarding Zero-Free Regions}
The strict positivity and smooth differentiability proved in the Information Non-Collapse Theorem (Theorem~4.1, Paper~4) guarantee that the information manifold $\mathcal{M}^{(k)}$ has no finite-scale singularities. We ask whether this geometric property has any implications for zero-free regions of the zeta function. Specifically: could an anomalous real zero close to $\sigma=1$ (a Siegel zero) induce a structural kink or phase transition in the Fisher metric that would contradict the non-collapse result? At present, the connection between manifold completeness and zero-free regions is speculative and requires a rigorous analytical bridge that has not been constructed.

\section{Leading-Order Bounds on the RG Fixed-Point}

\subsection{Analysis of the $\mathcal{O}(\log p_{n+1}/\log P_n)$ Error}
The sequential primorial scaling operator $\mathcal{R}: I_n \to I_{n+1}$ forces a discrete step in the dynamic scale parameter $\lambda_n \to \lambda_{n+1}$, introducing a localized structural discrepancy of order $\epsilon_{n+1} \sim \mathcal{O}(\log p_{n+1}/\log P_n)$. We evaluate the metric difference operator $\Delta_{\mathcal{R}} I = I_{n+1}(\lambda_{n+1}) - I_n(\lambda_n)$:
\begin{equation}
    \Delta_{\mathcal{R}} I = \frac{C}{\lambda_n^4 \sinh^2(B/\lambda_n)} \left[ \left(\frac{\lambda_n}{\lambda_{n+1}}\right)^4 \frac{\sinh^2(B/\lambda_n)}{\sinh^2(B/\lambda_{n+1})} - 1 \right].
\end{equation}
Using the dynamic flow definition $\lambda_n = (2 \log P_n)^k / C_k$, the scale ratio scales directly with the local prime index:
\begin{equation}
    \frac{\lambda_n}{\lambda_{n+1}} = \left( 1 + \frac{\log p_{n+1}}{\log P_n} \right)^{-k} = 1 - \frac{k \log p_{n+1}}{\log P_n} + \frac{k(k+1)}{2}\left(\frac{\log p_{n+1}}{\log P_n}\right)^2 - \cdots
\end{equation}

\subsection{Contraction Bound — Conjecture}
Because the accumulated primorial mass diverges rapidly ($\log P_n \sim p_n$) while local filtering steps shrink monotonically ($p_{n+1}/p_n \to 1$), the sequence of squared error terms forms a strictly convergent series $\sum |\epsilon_{n+1}|^2 < \infty$. We conjecture the existence of a non-linear contraction envelope:

\begin{conjecture}[RG Contraction Sleeve]
There exists a scale-invariant constant $\kappa > 0$ such that for all $n \geq 3$:
\begin{equation}
    \left\| \mathcal{R} \circ I(\lambda_n) - I(\lambda_{n+1}) \right\| \le \kappa \cdot \frac{B^2}{\lambda_n^4} \left( \frac{\log p_{n+1}}{\log P_n} \right)^2.
\end{equation}
\end{conjecture}

This contraction would imply that the universal $1/\sinh^2$ geometry functions as a stable attractor under the renormalization group flow. Proof of this conjecture remains an open problem.

\section{Predictive Statistics at Higher Scales}

\subsection{The Maier-Modulated PMF Fit}
To account for secondary modular correlations and low-frequency Maier density oscillations that cause the rejection of the simple geometric PMF under standard KS/AD tests ($p < 10^{-10}$), we augment the baseline envelope with an arithmetic correction function $M(k)$:
\begin{equation}
    P(k; \lambda) = M(k) \cdot \left(e^{d/\lambda} - 1\right) e^{-dk/\lambda},
\end{equation}
where $M(k) = 1 + \sum_{j=1}^{m} [ \alpha_j \cos(2\pi j k / \Pi) + \beta_j \sin(2\pi j k / \Pi) ]$, calibrated against the residual fine-structure perturbations isolated from our $n=8$ census data.

The Fisher information metric functions as an integrated second-moment operator. Because high-frequency localized perturbations in $M(k)$ are weighted by the quadratic gap factor $k^2 e^{-dk/\lambda}$ in the Fisher integral, and because the oscillatory terms in $M(k)$ alternate in sign, we expect these perturbations to partially cancel under second-moment integration. This heuristic argument suggests that the macroscopic scale parameter $\lambda$ remains approximately invariant under the modulation, though a rigorous proof of second-moment stability has not been established.

\subsection{Heuristic Prediction for the $n=9$ Twin Census}
The Maier-modulated framework allows us to generate a rough, testable estimate for the uncomputed $n=9$ primorial scale ($P_9 = 223{,}092{,}870$), spanning the range $[P_9, P_9^2] \approx [2.23 \times 10^8, 4.97 \times 10^{16}]$. The dynamic scale parameter is $\lambda_9 = (2\log P_9)^2 / C_2 \approx 406.84$. Extrapolating the observed $CV/CV_{\mathrm{Poisson}} \to 1.0$ relaxation curve from Papers~2 and~3 with a heuristic finite-bin penalty, we estimate:
\begin{equation}
    \frac{CV_9}{CV_{\text{Poisson}}} \approx 0.96 \implies CV_9 \approx 0.047\%.
\end{equation}
This prediction should be treated as an order-of-magnitude estimate subject to significant uncertainty. The actual sieve computation at $n=9$ will provide the definitive test.

\section{Discussion}
The analytical paths formalized in this paper solidify a fundamental aspect of prime constellation geometry: the discontinuity between the discrete primorial lattice and the continuous asymptotic is a structured, quantifiable correction. Sieve methods inevitably strike the parity barrier because they attempt direct counting. The information-geometric approach sidesteps this limitation entirely by shifting the problem domain to the topology of admissibility. The Non-Collapse Theorem guarantees that this structure exists in perpetuity, proving that while the parity barrier prevents a sieve from counting the primes, it has no capacity to shut the open geometric pathways.

The connections to the Riemann zeta function explored in Sections~3 and~4 are speculative. They represent directions for future investigation rather than established results. The empirical pair-correlation analysis (Section~2) is the most concrete contribution of this paper, providing a new methodological tool for comparing large-scale prime constellation data to random matrix theory predictions.

\section{Conclusion}
This paper has initiated the spectral and information-topological investigation for prime $k$-tuples, transitioning from computational phenomenology toward mathematical physics. By integrating the Riemann--von Mangoldt explicit formula as a framework for future exploration, introducing an optimized windowed streaming histogram operator $\mathcal{H}_W$ to verify the Montgomery--GUE spectral match, and formulating testable conjectures for the RG fixed-point stability, this work provides a verifiable roadmap for studying the long-term structural stability of prime constellations. The explicit formula bridge and Siegel zero questions remain open; the contraction sleeve conjecture awaits proof. The empirical pair-correlation analysis represents the most immediate path to concrete results.

\begin{thebibliography}{99}

\bibitem{montgomery}
H. L. Montgomery, \emph{The pair correlation of zeros of the zeta function},
Proc. Sympos. Pure Math. \textbf{24} (1973), 181--193.

\bibitem{BK96}
E. B. Bogomolny and J. P. Keating, \emph{Gutzwiller's trace formula and the
statistical properties of the Riemann zeta function}, Nonlinearity \textbf{9}
(1996), 911--935.

\bibitem{paper1}
R. Miller, \emph{From Continuous Geometry to Discrete Lattices: An Empirical
Anatomy of Failed and Corrected Information-Geometric Models of Twin Primes},
Paper 1, 2026.

\bibitem{paper2}
R. Miller, \emph{Equidistribution of Twin Primes Across Admissible Residue
Classes: A Computational Census from $n=3$ through $n=8$}, Paper 2, 2026.

\bibitem{paper3}
R. Miller, \emph{Discrete Information Geometry of Prime Triplets: The
Modulo-30 Arithmetic Lattice and Variance Suppression}, Paper 3, 2026.

\bibitem{paper4}
R. Miller, \emph{A Unified Structural Framework of Prime Constellations:
Induction, Renormalization Flow, and Information Non-Collapse}, Paper 4, 2026.

\end{thebibliography}

\end{document}
