\documentclass[11pt]{article}
\usepackage{amsmath, amssymb, amsfonts, amsthm, geometry, bm, booktabs}
\usepackage[hidelinks]{hyperref}
\geometry{margin=1in}

\title{Equidistribution of Twin Primes Across Admissible Residue Classes: \\ A Computational Census from $n=3$ through $n=8$}
\author{Rob Miller}
\date{June 2026}

\newtheorem{conjecture}{Conjecture}
\newtheorem{remark}{Remark}

\begin{document}
\maketitle

\begin{abstract}
We present a full computational census of twin prime distributions across all twin-admissible residue classes modulo $P_n$ for $n = 3$ through $n = 8$, where $P_n = \prod_{i=1}^n p_i$ is the $n$th primorial. At $n=8$ ($P_8 = 9{,}699{,}690$), we enumerate all 378{,}675 twin-admissible classes across the range $[P_8, P_8^2] \approx [9.7 \times 10^6, 9.4 \times 10^{13}]$ --- a 94-trillion-integer parallelised segmented sieve in 95.56 core-hours. We find that twin primes distribute across admissible classes with a sub-Poisson coefficient of variation: CV = 0.15\% at $n=8$, below the Poisson baseline of 0.17\%, with zero classes empty. The bias between expected and actual total twin-pair count is $<0.001\%$ at $n=8$. The convergence from $n=3$ (CV 2.44\%) through $n=8$ (CV 0.15\%) is strictly monotonic and extends the variance suppression observed in the joint class occupancy conjecture into the $10^{14}$ scale. This census establishes the empirical foundation for studying equidistribution phenomena in prime $k$-tuple residue classes.
\end{abstract}

\noindent \textbf{MSC 2020:} 11N05, 11N35, 11Y11

\section{Introduction}
\label{sec:intro}

The Hardy--Littlewood $k$-tuples conjecture \cite{HL23} predicts that prime constellations distribute across their admissible residue classes proportionally to their singular series. For twin primes, this is governed by the twin prime singular series $\mathfrak{S}(2) \approx 0.66016$. The twin-admissible residue classes modulo $P_n$ are those $a \in (\mathbb{Z}/P_n\mathbb{Z})^\times$ such that $a, a+2$ are both coprime to all $p \leq p_n$. There are $A_n = \prod_{2 < p \leq p_n} (p-2)$ such classes.

A central question is whether these twin-admissible classes are uniformly populated, or whether arithmetic structure creates preferred classes. The joint class occupancy conjecture asserts equidistribution across all admissible classes. This paper provides empirical validation through a full computational census from $n=3$ ($P_3 = 30$, 3 classes) through $n=8$ ($P_8 = 9{,}699{,}690$, 378{,}675 classes), cross-verified against established aggregate twin prime counts \cite{Nic12}.

This paper is Paper~2 in a two-part research program:
\begin{itemize}
  \item Paper~1: The discrete information-geometric framework establishing the modulo-6 lattice structure and Fisher information metric for twin primes.
  \item \textbf{Paper~2 (this work):} The equidistribution census providing empirical validation across six primorial scales ($n=3$ through $n=8$).
\end{itemize}

\noindent\textbf{Relationship to companion paper.} The discrete Fisher information metric and lattice structure derived in Paper~1 supply the structural foundation for the equidistribution phenomenon studied here. The algebraic non-vanishing analysis in Paper~1 establishes admissibility at all scales, while the empirical results of this paper demonstrate that twin-admissible classes are uniformly occupied across these six primorial scales. Together, the two papers form a complete architecture: the discrete geometry defines the structure, and the census confirms the equidistribution.

\section{Joint Class Occupancy Conjecture}
\label{sec:occupancy}

The empirical data supports the following conjecture about uniform class occupancy for twin-admissible residues at all scales $n \geq 3$:

\begin{conjecture}[Joint Class Occupancy Conjecture]
\label{conj:joint}
For every $n \geq 3$ and every twin-admissible residue class $a \in \mathcal{A}_n$ (where $\mathcal{A}_n$ is the set of $A_n$ twin-admissible classes modulo $P_n$), the twin prime pair count $\pi_2(x; P_n, a) > 0$ for all $x \geq P_n^2$. In other words, no twin-admissible class is empty.
\end{conjecture}

\noindent Our full census at $n=8$ confirms this conjecture empirically: with 378{,}675 classes across 94 trillion integers, zero classes were empty. The minimum occupancy across all classes was 336{,}256 twin pairs and the maximum was 340{,}861 pairs (a tight $\sim 1.3\%$ spread around the mean of 338{,}680). The joint occupancy across the entire range was 128{,}249{,}570{,}494 twin pairs.

\section{Methodology}

\subsection{Segmented Sieve Architecture}

The census was performed using a parallelised segmented sieve over $[P_n, P_n^2]$. For $n=8$ ($P_8 = 9{,}699{,}690$, range $[P_8, P_8^2] \approx 9.4 \times 10^{13}$), we used $\sim 115$ million 1 MB segments distributed across 8 threads. Each segment sieves using all base primes from 3 up to $\sqrt{P_8^2} = P_8$, then identifies twin pairs within each twin-admissible residue class.

\subsection{Classification and Binning}

For each twin pair $(p, p+2)$ found in $[P_n, P_n^2]$, we classify the pair by its residue $p \bmod P_n$. Only twin-admissible classes ($a$ such that $a, a+2$ are both coprime to $p_i$ for all $i \leq n$) are tracked. The census counts the number of twin pairs in each class, producing a histogram of length $A_n$ from which we compute:
\begin{itemize}
  \item Total twin-pair count (sum over all classes)
  \item Mean pairs per class $= \text{Total} / A_n$
  \item Coefficient of variation $= 100 \times \sigma / \mu$
  \item Minimum and maximum occupancy
  \item Number of empty classes
\end{itemize}

\section{Results}
\label{sec:results}

\subsection{Census Table}

\begin{table}[h]
\centering
\caption{Equidistribution of primes across twin-admissible classes mod $P_n$ over range $[P_n, P_n^2]$.}
\label{tab:numerical}
\begin{tabular}{cccccccc}
\toprule
$n$ & $P_n$ & $A_n$ & Total Pairs & Mean ($\mu$) & $|\text{Bias}|$\% & CV & CV$_{\text{rand}}$ \\
\midrule
3 & 30 & 3 & 30 & 10.0 & 30.21 & 16.33 & 31.62 \\
4 & 210 & 15 & 621 & 41.4 & 5.22 & 7.68 & 15.54 \\
5 & 2{,}310 & 135 & 34{,}196 & 253.3 & 0.01 & 4.68 & 6.28 \\
6 & 30{,}030 & 1{,}485 & 3{,}120{,}435 & 2{,}101.3 & 0.05 & 1.69 & 2.18 \\
7 & 510{,}510 & 22{,}275 & 541{,}042{,}776 & 24{,}289.2 & $<0.001$ & $0.53^{\dagger}$ & 0.64 \\
\textbf{8} & \textbf{9{,}699{,}690} & \textbf{378{,}675} & \textbf{128{,}249{,}570{,}494} & \textbf{338{,}680.1} & \textbf{$<$0.001} & \textbf{0.15} & \textbf{0.17} \\
\bottomrule
\end{tabular}

\vspace{0.5em}
\noindent{\footnotesize $^{\dagger}$ At $n=7$, the range of class counts was [23{,}779, 24{,}781].
CV$_{\mathrm{rand}} = 100/\sqrt{\mu}$ represents the independent Poisson baseline. Bias is calculated against the cumulative Hardy--Littlewood prediction $2C_2\,\mathrm{li}_2(P_n^2)$.
}
\end{table}

\noindent At $n=8$, we computed all 378{,}675 twin-admissible classes across the full range $[P_8, P_8^2] \approx [9.7 \times 10^6, 9.4 \times 10^{13}]$ --- a 94-trillion-integer census performed by a parallelised segmented sieve in 95.56 core-hours. The bias is below 0.001\% (error of 813{,}232 among 128 billion twin pairs), the coefficient of variation is 0.15\% (below the Poisson baseline of 0.17\%), and zero classes were empty. This extends the sub-Poisson variance suppression observed since $n=3$ into the $10^{14}$ scale.

\subsection{Interpretation of the CV Baseline and Multinomial Constraints}

The independent Poisson baseline CV$_{\text{rand}} = 100/\sqrt{\mu}$ represents the expected coefficient of variation if twin pairs were distributed across classes as independent random events. At $n=8$, $\mu \approx 338{,}680$, giving CV$_{\text{rand}} \approx 0.17\%$. 

Because the total number of twin pairs in the interval is fixed, the baseline distribution of class counts is technically multinomial rather than independent Poisson. The multinomial variance is $\sigma^2 = \mu(1 - 1/A_n)$. However, because the number of admissible classes $A_n$ grows so rapidly, this fixed-total constraint has a vanishingly small effect. At $n=8$ ($A_8 = 378{,}675$), the multinomial constraint reduces the expected CV by a factor of $\sqrt{1 - 1/378{,}675} \approx 0.999998$. 

Therefore, the multinomial constraint accounts for a negligible fraction of the variance reduction. The observed CV of 0.15\% (a $\sim 15\%$ suppression below the baseline) represents genuine structural anti-clumping across the primorial lattice.

\section{Theta Sieve and Variance Suppression}
\label{sec:theta}

The Theta Sieve methodology provides a computational tracking framework for understanding why twin primes show sub-Poisson variance across admissible classes. The sieve identifies regions of arithmetic space where the twin pair density is suppressed relative to random expectation. At $n=8$, the 0.15\% CV represents a stable variance suppression of $\sim 15\%$ below the Poisson baseline of 0.17\%, consistent with the trend observed from $n=3$ through $n=7$.

This sub-Poisson variance pattern suggests that twin primes are not merely distributed randomly across admissible classes \cite{Bre14}, but exhibit a structural anti-clumping behavior that becomes more pronounced at larger primorial scales \cite{Mai85}. This suppression may reflect the same arithmetic rigidity captured by the modulo-6 lattice structure in Paper~1, but the direct analytical connection remains an open area of inquiry.

\section{Algorithmic Implementation}
\label{sec:implementation}

\subsection{Parallelization Architecture}

The census is inherently parallelizable: each segment of integers is processed independently. The implementation distributes work across $T$ threads, each processing a contiguous segment of the range $[P_n, P_n^2]$. For $n=8$, we used 8 threads, each processing $\sim 14.5$ million segments. Each thread maintains a local counter for each twin-admissible residue class, and final aggregation combines the per-thread counts via reduction.

\subsection{Segmented Processing}

For ranges exceeding available memory, the interval is partitioned into segments of fixed size (typically 1 MB for $n=8$). Each segment is sieved independently using all base primes up to $\sqrt{\text{upper}}$, with cross-segment boundaries handled by extending each segment by two positions to capture twin pairs that straddle the boundary. This mirrors the boundary correction methodology established in the discrete information-geometric framework of Paper~1.

\section{Conclusion}
\label{sec:conclusion}

The full census of twin-admissible residue classes from $n=3$ through $n=8$ confirms that twin primes distribute uniformly across admissible classes with a sub-Poisson coefficient of variation at all scales studied. At $n=8$ ($P_8 = 9{,}699{,}690$), the census found all 378{,}675 classes occupied with CV 0.15\%, below the Poisson baseline of 0.17\%, across 128 billion twin pairs in a 94-trillion-integer range. Zero classes were empty, confirming the joint class occupancy conjecture empirically out to $X = 9.4 \times 10^{13}$.

Combined with the discrete information-geometric framework (Paper~1), which establishes the permanent statistical structure of the twin prime distribution on the modulo-6 lattice, this census provides the empirical foundation for studying equidistribution phenomena in prime $k$-tuples. The methodology scales to higher-order constellations (prime triplets on mod-30 lattices, etc.), where the tighter modular constraints are expected to produce even more pronounced structural effects.

\subsection*{Acknowledgments}

Sieve implementations, computational results, and LaTeX source for this paper are available at \url{https://github.com/rnmbaker-spec/rapf-prime-framework}.

The sieve implementations, computational results, and LaTeX typesetting were developed with the assistance of automated computational tools.

\begin{thebibliography}{9}

\bibitem{HL23}
G. H. Hardy and J. E. Littlewood,
\textit{Some problems of ``Partitio numerorum'' III: On the expression of a number as a sum of primes},
Acta Math. \textbf{44} (1923), 1--70.

\bibitem{Mai85}
H. Maier,
\textit{Primes in short intervals},
Michigan Math. J. \textbf{32} (1985), 221--225.

\bibitem{Bre14}
R. P. Brent,
\textit{Twin primes (seem to be) more random than primes},
ANU Workshop (2014). Slides available at \url{https://maths-people.anu.edu.au/~brent/pd/twin_primes_and_primes.pdf}.

\bibitem{Gal76}
P. X. Gallagher,
\textit{On the distribution of primes in short intervals},
Mathematika \textbf{23} (1976), 4--9. Corrigendum, \textbf{28} (1981), 86.

\bibitem{Nic12}
W. D. Nicely,
\textit{Twin primes},
\url{https://t5k.org/lists/2small/}, computed values of $\pi_2(X)$.

\bibitem{CR48}
H. Cram\'{e}r,
\textit{Mathematical Methods of Statistics},
Princeton University Press (1948).

\end{thebibliography}

\end{document}
